Timely Object Recognition

### 2012-03-05 writeups/eccv12/eccv12.tex
draft
people's ocmment

\title{Timely Object Detection}

@@

\begin{abstract}
In a large, multi-class detection system, the problem of timeliness of results is crucial.
We are motivated by situations where running all detectors would take an unacceptably long time, and the best answer must be given by some deadline.
Our system for multi-class detection aims to give the best possible results at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic policy to decide which detector to deploy next.
The policy is guided by an estimate of the contents of the image, and is sensitive to the time deadline and the ``value'' of different classes.
We evaluate parametrizations of the policy with respect to performance in the novel AP vs. Time evaluation on the PASCAL VOC dataset.
\end{abstract}

@@

\bibliographystyle{splncs}
\bibliography{sergeyk-bibtex}

>>>>

\title{Timely Object Recognition}

@@

\begin{abstract}
\todo{put the word visual somewhere}
In a large, multi-class detection system, the problem of timeliness of results is crucial.
We are motivated by situations where running all detectors would take an unacceptably long time, and that the best answer must be given by some deadline.
Our system for multi-class detection aims to give the best possible results at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic policy to decide which detector to deploy next.
The policy is guided by an estimate of the contents of the image, and is sensitive to the time deadline and the ``value'' of different classes.
We evaluate parametrizations of the policy with respect to performance in the novel AP vs. Time evaluation on the PASCAL VOC dataset.
\end{abstract}

@@

\bibliographystyle{splncs}
\bibliography{sergeyk-bibtex,misc}

### 2012-03-05 writeups/eccv12/technical.tex
people's ocmment

Our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$ and a list of multi-class detection results $\emph{detect}(I)$.

@@

A dynamic, or ``closed-loop,'' policy bases action selection on observations received from previous actions, exploiting the signal in inter-object and scene context for a maximally efficient path through the actions.
This is our goal, and what sets our formulation apart from multi-class systems that evaluate in a fixed order, such as simple cascades \cite{Viola2001} or \todo{add another one}.

@@

As shown in Figure~\ref{fig:evaluation}, the system is given two times: the setup time $T_s$ and deadline $T_d$.
From the setup time to the deadline, we want to obtain the best possible answer if stopped at any given time.
This corresponds to the general notion of Anytime algorithms, and is motivated by desired flexibility in the system.

@@

\begin{table}[h!]
\centering
\caption{Summary of the notation.}
\label{tab:notation}
\begin{tabular}{|l|l|}
  \hline
  $\mathcal{I}$ & image \\
  $C_k$         & presence of class $k \in \{1,\dots,K\}$ \\ 
  $t$           & time into episode \\ 
  $T_s$, $T_d$  & start and deadline times \\ 
  $b^j$         & belief state at step $j$ \\ 
  $\pi$         & policy function, $b \mapsto a \in \mathcal{A}$ \\
  $\mathcal{A}$ & set of actions $a_i \in \{\mathcal{L} \cup \mathcal{F}\}$\\ 
  $\mathcal{F}$ & set of featurization actions \\
  $\mathcal{L}$ & set of classification actions\\
  $o_i$         & a real-valued observation upon executing $a_i \in \mathcal{L}$\\
  $\mathcal{O}$ & set of executed actions\\
  $\mathbf{o}$  & set of observations $\{o_i | a_i \in \mathcal{O}\}$\\
  $c(a_i)$        & cost of executing $a_i$, in units of $t$\\
  \hline
\end{tabular}\end{table}

@@

Specifically, as shown in Figure~\ref{fig:rewards}, we define the reward of an action as
\begin{equation}\label{eq:advanced}
R(b^j,a_i) = \frac{\Delta \text{ap}_i (t_T^j-\frac{1}{2}\Delta t_i)}{(1-\text{ap}_i)t_T^j}
\end{equation}
where $t_T^j$ is the time left until deadline at state $b^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.

>>>>

As presented in Figure~\ref{fig:pomdp}, our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$ and a list of multi-class detection results $\emph{detect}(I)$.

@@

A dynamic, or ``closed-loop,'' policy bases action selection on observations received from previous actions, exploiting the signal in inter-object and scene context for a maximally efficient path through the actions.
This is our goal, and what sets our formulation apart from multi-class systems that evaluate in a fixed order, such as simple cascades \cite{Viola2001} or decision trees.

@@

As shown in Figure~\ref{fig:evaluation}, the system is given two times: the setup time $T_s$ and deadline $T_d$.
From the setup time to the deadline, we want to obtain the best possible answer if stopped at any given time.
This corresponds to the general notion of \emph{Anytime} algorithms, and is motivated by desired flexibility in the system.

@@

\begin{table}[h!]
\centering
\caption{Summary of the notation.}
\label{tab:notation}
\begin{tabular}{|l|l|}
  \hline
  $\mathcal{I}$ & image \\
  $C_k$         & presence of class $k \in \{1,\dots,K\}$ \\ 
  $t$           & time into episode \\ 
  $T_s$, $T_d$  & start and deadline times \\ 
  $b^j$         & belief state at step $j$ \\ 
  $\pi$         & policy function, $b \mapsto a \in \mathcal{A}$ \\
  $\mathcal{A}$ & set of actions $a$\\ 
  \comment{$\mathcal{F}$ & set of featurization actions \\}
  \comment{$\mathcal{L}$ & set of classification actions\\}
  $o_i$         & a real-valued observation upon executing $a_i \in \mathcal{A}$\\
  $\mathcal{O}$ & set of executed actions\\
  $\mathbf{o}$  & set of observations $\{o_i | a_i \in \mathcal{O}\}$\\
  $c(a_i)$        & cost of executing $a_i$, in units of $t$\\
  \hline
\end{tabular}\end{table}

@@

Specifically, as shown in Figure~\ref{fig:rewards}, we define the reward of an action as
\begin{equation}\label{eq:advanced}
R(b^j,a_i) = \frac{\Delta \text{ap}_i (t_T^j-\frac{1}{2}\Delta t_i)}{(1-\text{ap}^j)t_T^j}
\end{equation}
where $t_T^j$ is the time left until deadline at state $b^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.
